Let's Play Congestion Control

### 2017-10-04 tex/paper.tex
Add new config files

  \begin{scope}
    \node [place,tokens=1] (s1) at (2,4) [label=Received feedback] {};
    \node [place,tokens=1] (s2) at (2,0) [label={[align=center]below:Open\\congestion\\window}] {};

    \node [transition] (e2) at (0,2) [label=left:Take action] {}
      edge [post,bend right] node {$a$}(s2)
      edge [pre,bend left] node {1} (s1);

>>>>

  \begin{scope}
    \node [place,tokens=1] (s1) [label=Received feedback] {};
    \node [place] (s2) [below of=s1, label=Network] {};
    \node [place,tokens=1] (s3) [below of=s2, label={[align=center]below:Open\\congestion\\window}] {};

    \node [transition] (e2) [left of=s2, label=left:Take action] {}
      edge [post,bend right] node {$a$}(s3)
      edge [pre,bend left] node {1} (s1);
